DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-04 paper/evaluation.tex
eval C. revision

\subsection{Multicore Performance}
It may not always be the case that all four cores of the Raspberry Pi 3's Cortex A-53 CPU can be used 
solely for the purpose of operating an autonomous vehicle. Thus, we test how the number of cores 
utilized for real-time operations affects the DeepPicar's overall ability to function as an autonomous 
vehicle platform.

\begin{table}[h]
  \centering
  \begin{tabular} {| l | l | l | l | l | l | l | l | l | l |}
    \hline
    \textbf{num cores} & \textbf{mean} & \textbf{max} & \textbf{99pct} & \textbf{stdev} \\ \hline 
    1 & 61.96 & 66.00 & 63.31 & 0.51\\ \hline
    2 & 50.49 & 71.55 & 70.03 & 3.16 \\ \hline
    3 & 48.11 & 72.22 & 58.45 & 4.18 \\ \hline
    4 & 42.67 & 56.37 & 50.70 & 2.80 \\
    \hline
  \end{tabular}
  \caption{Real-time performance of DeepPicar depending on the number of cores used.}
\end{table}

The performance of the DeepPicar is summarized in Table III. The DeepPicar performed better, on average, 
when it utilized more cores. With 4 cores, it was able to meet the vast majority of its deadlines, doing 
so in almost 99\% of the input frames. The platform performed the worst when using only 1 core, 
as it was unable to meet any of its deadlines.  On average, using 3 cores instead of 2 only had a 
performance increase of approximately 2 ms, so the addition of one core in that specific case offers 
relatively little improvement. One important observation is that the performance was more consistent 
when only 1 core was used. As a result, the use of multiple cores is very beneficial in terms of 
reducing the time it takes to complete inference operations, but may result in times that are more 
volatile.

>>>>

\subsection{Effect of the Core Count to Inference Timing}

In this experiment, we investigate the scalability of performing
inference operation of DeepPicar's nueral network with respect to the
number of cores. As noted earlier, the Raspberry Pi 3 platform has
four Cortex-A53 cores and the Tensorflow 
provides a programmable mechanism to to adjust how many cores to be
used by the library. Leveraging this feature, we repeat the
same experiment described in the previous subsection with varying
number of CPU cores---from one to four.

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/perf_vs_corecnt}
  \caption{Average control loop execution time vs. \#of CPU
    cores. \fixme{instead of the total control loop time, use the
      average of DNN inferencing time.}}
  \label{fig:perf-vs-corecnt}
\end{figure}

%% \begin{table}[h]
%%   \centering
%%   \begin{tabular} {| c | l | l | l | l | l | l | l | l | l |}
%%     \hline
%%     \textbf{\#of cores} & \textbf{Mean} & \textbf{Max} & \textbf{99pct} & \textbf{Stdev} \\ \hline 
%%     1 & 61.96 & 66.00 & 63.31 & 0.51\\ \hline
%%     2 & 50.49 & 71.55 & 70.03 & 3.16 \\ \hline
%%     3 & 48.11 & 72.22 & 58.45 & 4.18 \\ \hline
%%     4 & 42.67 & 56.37 & 50.70 & 2.80 \\
%%     \hline
%%   \end{tabular}
%%   \caption{Execution time statistics vs. \#of CPU cores.}
%% \end{table}

Figure~\ref{fig:perf-vs-corecnt} shows the average execution times of
the control loop as we vary the number of cores used by the
Tensorflow. As expected as we assign more cores, the average execution
time decreases---from 61.96 ms on a single core to 42.67 ms on four
cores. However, the improvement is far from being ideal as we expected
linear scaling. In particular, from 2 cores to 3 cores, the
improvement is mere 2.38ms (or 4\%). In short, we find that the
scalability of DeepPicar's deep neural network is not ideal on the
platform. We do not know whether it is due to the limitations of
Tensorflow's multicore implementation or it's the model's inherent
characteristics.

The poor scalability opens up the possibility of consolidating
multiple different tasks or different nueral network models rather
than allocating all cores for a single nueral network model. For
example, it is conceivable to use four cameras and four different
neural network models, each of which is trained seperately and
executed on a single dedicated core. Assuming we use the same network
architecture for all models, then one might exepct to achieve up to
15 Hz using one core (given 1 core can deliver 62ms average
execution time). In the next experiment, we investigate the
feasibility of such a scenario.

%% It may not always be the case that all four cores of the Raspberry Pi
%% 3's Cortex A-53 CPU can be used solely for the purpose of operating an
%% autonomous vehicle. Thus, we test how the number of cores utilized for
%% real-time operations affects the DeepPicar's overall ability to
%% function as an autonomous vehicle platform.

%% The performance of the DeepPicar is summarized in Table III. The
%% DeepPicar performed better, on average, when it utilized more
%% cores. With 4 cores, it was able to meet the vast majority of its
%% deadlines, doing so in almost 99\% of the input frames. The platform
%% performed the worst when using only 1 core, as it was unable to meet
%% any of its deadlines.  On average, using 3 cores instead of 2 only had
%% a performance increase of approximately 2 ms, so the addition of one
%% core in that specific case offers  relatively little improvement. One
%% important observation is that the performance was more consistent when
%% only 1 core was used. As a result, the use of multiple cores is very
%% beneficial in terms of reducing the time it takes to complete
%% inference operations, but may result in times that are more volatile.
